Radiance - A Web Application Environment

### 2016-12-16 els2017-radiance/paper.tex
Some measly references

\begin{abstract}
  Radiance is a set of libraries that together provide an environment for web applications. Unlike traditional web frameworks that focus on a set of tools to support the construction and maintenance of a single application, Radiance attempts to allow you to run as many differing applications as desired in the same environment. This has many advantages, as frequently there are common resources in applications that should be shared between them, but cannot because the applications are separated and developed without regard for sharing. In order to fix this, Radiance provides an extensible interface mechanism to standardise the interaction between users of common resources. To facilitate the separation and encapsulation of the shared URL address space between applications, Radiance also provides a flexible routing mechanism. This mechanism is powerful enough to ensure that any application written with Radiance can be deployed on any server setup, no matter how complicated the constraints, without needing to change the source code of the application.
\end{abstract}

@@

A web application framework is comprised of several components. This can go from the absolute minimum of an HTTP server and URL dispatch mechanism as seen in microframeworks, to a vast range of tools including database access, authentication, user management, validation, API endpoints, etc. All of the components exist with the aim of reducing the amount of work necessary to write a specific web application. \\

@@

If an (untranslated) request to \texttt{hello/index} is performed, the above code will be executed, and the template system Clip will render the \texttt{index.ctml} file. The template might look as follows:

@@

%\bibliography{els2017-radiance}
\end{document}

>>>>

\begin{abstract}
  Radiance\cite{radiance} is a set of libraries that together provide an environment for web applications. Unlike traditional web frameworks that focus on a set of tools to support the construction and maintenance of a single application, Radiance attempts to allow you to run as many differing applications as desired in the same environment. This has many advantages, as frequently there are common resources in applications that should be shared between them, but cannot because the applications are separated and developed without regard for sharing. In order to fix this, Radiance provides an extensible interface mechanism to standardise the interaction between users of common resources. To facilitate the separation and encapsulation of the shared URL address space between applications, Radiance also provides a flexible routing mechanism. This mechanism is powerful enough to ensure that any application written with Radiance can be deployed on any server setup, no matter how complicated the constraints, without needing to change the source code of the application.
\end{abstract}

@@

A web application framework is comprised of several components. This can go from the absolute minimum of an HTTP server and URL dispatch mechanism as seen in microframeworks\cite{microframeworks}, to a vast range of tools including database access, authentication, user management, validation, API endpoints, etc. All of the components exist with the aim of reducing the amount of work necessary to write a specific web application. \\

@@

If an (untranslated) request to \texttt{hello/index} is performed, the above code will be executed, and the template system Clip\cite{clip} will render the \texttt{index.ctml} file. The template might look as follows:

@@

\bibliography{paper}
\end{document}
